Twists of supersymmetric gauge theories

### 2019-09-04 paper.tex
8d interaction sketch calculation

The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.  If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$.  The BRST fields decompose as
\begin{align*}
A &\mapsto A_{0,1} + A_{1,0} + \chi^0_1 + \chi^0_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+_1 + \chi^+_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^-_1 + \chi^-_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
\end{align*}
along with the ghost $c$ and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.  In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.  We choose the two supercharge $Q_{\mr{hol}}$ and $Q'$ to each be pure individually, but to have impure sum.  The action of such a supercharge can be written in terms of a quadratic and a cubic interaction as
\begin{align*}
I^{(1)}_t &= \\
I^{(2)}_t &= .
\end{align*}

@@

\begin{proof}

\end{proof}

>>>>

The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.  If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$.  The BRST fields decompose as
\begin{align*}
A &\mapsto A_{0,1} + A_{1,0} + \chi^0_1 + \chi^0_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+_1 + \chi^+_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^-_1 + \chi^-_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
\end{align*}
along with the ghost $c$ and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.  In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.  We choose the two supercharge $Q_{\mr{hol}}$ and $Q'$ to each be pure individually, but to have impure sum.  The action of such a supercharge can be written in terms of a quadratic and a cubic interaction as
\begin{align*}
I^{(1)}_t &= \int \langle A_{1,0}^\vee, \psi_{1,0}^- + t\psi_{1,0}^+\rangle + \langle \phi_1^\vee, \chi_1^+ + t\chi_1^- \rangle + \langle \phi_2^\vee, \chi_2^- + t\chi_2^+ \rangle + \langle (\chi_1^-)\vee + t(\chi_1^+)^\vee, \Lambda F_{1,1} \rangle + \\
&\quad + \langle (\psi^-_{1,0})^\vee + t(\psi^+_{1,0})^\vee, F_{0,2} \rangle + \langle (\psi^-_{0,1})^\vee + t(\psi^+_{0,1})^\vee, \ol \dd_{A_{0,1}} (\phi_1 + \chi_1^0) \rangle \\
I^{(2)}_t &= \int \langle (\chi_1^+)^\vee + t(\chi_1^-)^\vee, (\chi_1^+)^\vee \rangle.
\end{align*}
\chris{This is a bit of a mess, but it's a first pass guess, and I think it's correct for $t=0$.  I want to identify $F_{0,2}$ on a CY3 with a $(1,0)$ form.}

@@

\begin{proof}
\chris{Strategy: compute the holomorphic twist, as in 10d, and see which fields survive.  Then consider the perturbation of the twisted action.  Show that it doesn't change the fields that survive, maybe using a spectral sequence associated to the perturbation, and compute how the BV differential deforms.}
\end{proof}
